OpenMPIR

### 2017-10-06 paper.tex
fix spelling typo

The contributions of this work include
\begin{itemize}
  \item A prototype front end that transforms OpenMP task constructs to Tapir IR;
  \item Benchmarks of the implementation using a Cilk runtime back end, showing
        performance improvements over existing OpenMP implementations; and
  \item An initial investigation into the reasons for these performance improvements.
\end{itemize}
Our hope is to move the community towards further conversations on a 
shared IR that can be used for many programming models. The work presented here only
represents a small step in that direction and there is still a herculean amount
of design and implementaton details to be considered. We argue that the benefits vastly outweigh 
the costs and we hope to see future work explore additional possibilities.

>>>>

The contributions of this work include
\begin{itemize}
  \item A prototype front end that transforms OpenMP task constructs to Tapir IR;
  \item Benchmarks of the implementation using a Cilk runtime back end, showing
        performance improvements over existing OpenMP implementations; and
  \item An initial investigation into the reasons for these performance improvements.
\end{itemize}
Our hope is to move the community towards further conversations on a 
shared IR that can be used for many programming models. The work presented here only
represents a small step in that direction and there is still a herculean amount
of design and implementation details to be considered. We argue that the benefits vastly outweigh 
the costs and we hope to see future work explore additional possibilities.
